---
title: "MGM"
output: html_document
date: '2022-10-05'
---
# Packages
```{r message=FALSE, warning=FALSE, include=FALSE}
library(stats)
library(rio)
library(tidyverse)
library(dplyr)
library(lavaan)
library(mgm) 
library(qgraph)
library(dplyr)
library(haven)
library(Matrix)
library(igraph)
library(NetworkComparisonTest)
library(plyr)
library(bootnet)
library(openxlsx)
library(matrixcalc)
library(IsingSampler)
library(IsingFit)
library(xtable)
library(ltm)
```

# Import MGM
```{r}
MGM <- import("../input/MGM.csv")
```

# Create objects
```{r}
type <-c(
  "c","g","c","g","c",
  "g","g","g","g","c",
  "c","c","g","c","g",
  "g","g","g","g","g",
  "g","g")

level <-c(
  2,1,2,1,2,
  1,1,1,1,2,
  2,2,1,2,1,
  1,1,1,1,1,
  1,1)

shortnames <- c(
  "sex",
  "age",
  "inc",
  "agm",
  "res",
  "eco",
  "htr",
  "Con",
  "hap",
  "hea",
  "anx",
  "dep",
  "LR",
  "int",
  "comp_",
  "w2r_",
  "in_tr_",
  "risk_",
  "col_",
  "reg_",
  "sci_",
  "med_")

longnames <- c(
  "Sex",
  "Age",
  "Family income",
  "Approval governmental measures",
  "Approval restrictive measures",
  "Economy over public health",
  "Horizontal trust",
  "Support for Conte",
  "Happiness",
  "Health",
  "Anxiety",
  "Depression",
  "L-R self-placement",
  "Political interest",
  "Compliance to preventive behaviors",
  "Willingness to restrict freedoms",
  "Institutional trust",
  "Risk perception",
  "Collectivism",
  "Support for regional system",
  "Attitudes toward science",
  "Attitudes toward medicine")
```

# Fit model
```{r}
set.seed(1)
FitMGM <- mgm(MGM, type, level, k = 2, binarySign = TRUE)
```

# Preliminary graphs
Now I ll do a raw graph, basically community detection is missing, and I have to 
apply a cut of. 
```{r}
#raw graph
set.seed(1)
qgraph(FitMGM$pairwise$wadj, 
       layout = "spring",
       theme = "colorblind",
       edge.color = FitMGM$pairwise$edgecolor,
       labels = shortnames, nodeNames = longnames, vsize=6.0,
       title = "Raw graph", edge.labels=FALSE, 
       legend = TRUE, legend.cex = 0.3)


```

# Community detection
```{r}
##Create function Community stability
communityStability <- function(data, type, level, iterations)
{
  
  communityMemberships <- list()
  
  for (i in 1:iterations)
  {
    fitGraph <- mgm(data, type, level, k = 2, verbatim = TRUE)
    iGraph<- graph_from_adjacency_matrix(abs
                                         (fitGraph$pairwise$wadj), "undirected", weighted =
                                           TRUE)
    communityMemberships[[i]] <- cluster_walktrap(iGraph)$membership
  }
  
  communityOverlap <- matrix(NA, length(data), length(data))
  
  for(j in 1:length(data))
  {
    
    overlapPerNode <- matrix(NA, iterations, ncol(communityOverlap))
    
    for(k in 1: iterations)
    {
      overlapPerNode[k,] <- as.numeric(communityMemberships[[k]][j] == communityMemberships[[k]])
    }
    
    communityOverlap[j,] <- apply(overlapPerNode, 2, mean)
  }
  
  diag(communityOverlap) <- 0
  
  return(list(communityMemberships = communityMemberships, communityOverlap = communityOverlap))
  
}
```

Now I apply the function. I reduce the number of iteration from 1000 to 100 
due to my limited computational power.
```{r}
#apply function
CommunityStabTotal<-communityStability(MGM, type, level, it=100)
```

```{r}
# Visualize community stability
pdf(file = '../Output/MGM/community stability MGM.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(CommunityStabTotal$communityOverlap, layout = "spring", 
       theme = "colorblind", labels = shortnames,
       nodeNames = longnames,vsize=4.0,
       title = "Community Stability MGM", 
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
dev.off()
```
```{r}
# Vizualise detected communities
inputCommDetection_total<-CommunityStabTotal$communityOverlap
inputCommDetection_total[which(inputCommDetection_total <= .90)] <- 0

pdf(file = '../Output/MGM/detected communities MGM.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(inputCommDetection_total, layout = "spring", theme = "colorblind",
       labels = shortnames, nodeNames = longnames,vsize=4.0,
       title = "Detected communities MGM", edge.labels=FALSE, 
       legend = TRUE, legend.cex = 0.3)
dev.off()
```
```{r}
# group variables based on outcome detection community stability so we can assign colors
Totalgroup_comm <- list(
 " "=c(2,3,9,10,18),
 " "=c(4,8),
 " "=c(11,12),
 " "=c(1,5,6,7,13,14,15,16,17,19,20,21,22))
```

```{r}
# define nice colors
Totalgroup_cols <- c("#E8ED61","#E35959","#4B71B3","#8FC45A")
```

# Final graphs
```{r}
#a better graph (only communities missing)
#enables theme colorblind because we don't need to specify edge.color
inputGraphMGM <- FitMGM$pairwise$wadj
signsGraphMGM <- FitMGM$pairwise$signs
signsGraphMGM[which(is.na(signsGraphMGM))] <- 1
inputGraphMGM <- inputGraphMGM*signsGraphMGM

# refined, no minimum 
pdf(file = '../Output/MGM/MGM no min.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.4)
dev.off()

# refined,  minimum = 0.5
pdf(file = '../Output/MGM/MGM min 0.05.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.05, maximum = 1, 
  details = FALSE, vsize=6.0, 
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.4)
dev.off()

# refined,  minimum = 0.10
pdf(file = '../Output/MGM/MGM min 0.10.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, legend = TRUE,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend.cex = 0.4)
dev.off()
```
# Centrality estimates
```{r}
#graph with complete labels for centrality plot
GraphMGMCENT<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind",
  labels = longnames, minimum = 0,
  cut = 0.10, maximum = 1, details = TRUE,
  legend = FALSE, title = "Centrality table")

#centrality Total
centMGM <- centralityTable(GraphMGMCENT,standardized = FALSE)

#CentralityPlot Total
pdf('../Output/MGM/Centrality Table MGM.pdf')
centralityPlot(GraphMGMCENT, include = c("Strength"),scale = "raw",
               orderBy = "Strength")
dev.off()

```
# ASPL
```{r}
#Shortest Path Lenght
SPLMGM <- centrality(GraphMGM)$ShortestPathLengths
SPLMGM <- SPLMGM[upper.tri(SPLMGM)]
#Average shortest path length
ASPL_MGM <- mean(SPLMGM)
```
ASPL = 11.53732


# Stability of centrality measures
Say you spot a node to be more central than other nodes. What is the stability 
of the centrality estimates? Let's assess stability of the centrality index by 
case-dropping subset bootstrap
I reduce nBoots to 100, not 1k
```{r}
set.seed(1)
MGM_CentStability <- bootnet(MGM, nBoots = 100, 
default = "mgm", type = "case",
statistics = c("Strength"), level = level, criterion="CV", binarySign=FALSE)
corStability(MGM_CentStability)

#plot
plot(MGM_CentStability, subsetRange = c(100,50), statistics = c("Strength"),
     labels = longnames)

#plot ordered
pdf('../Output/MGM/Centrality stability MGM.pdf', height = 70, width = 50)
plot(MGM_CentStability, "Strength", perNode = TRUE, labels = longnames,
     subsetRange = c(100,50))
dev.off()

```

# Accuracy
Say you spot a difference in edges, one thicker than the other: 
Is it meaningfully stronger? Check accuracy assess the accuracy of estimated
network connections --> Obtain confidence interval around estimated edge weight
using nonparametric bootstrapping. I reduce again the nBoots from 1k to 100

```{r}
#Edge accuracy Total
set.seed(1)
Bootnet_MGM<- bootnet(MGM, nBoots = 100, 
default = "mgm", level = level, criterion="CV", binarySign=FALSE, 
labels = longnames)

#pdf
pdf('../Output/MGM/Edge accuracy MGM.pdf', height = 50, width = 50)
plot(Bootnet_MGM, labels = TRUE, order = "sample", res=150)
dev.off()

```
# Edge weight to Excel
```{r}
##only upper triangle without edge weigths 0 for readability
EdgeWeight_Total_half<-upper.triangle(inputGraphMGM)
EdgeWeight_Total_half[EdgeWeight_Total_half == 0] <- NA
EdgeWeightsExcel_half<- list("mgm" = EdgeWeight_Total_half)
write.xlsx(EdgeWeightsExcel_half, "../Output/MGM/EdgeWeightsExcel_half.xlsx", 
           colWidths = "auto", rowNames = TRUE)

```

