---
title: "MGM_G"
output:
  html_document: default
  pdf_document: default
date: '2022-10-07'
---
# Packages
```{r message=FALSE, warning=FALSE, include=FALSE}
library(stats)
library(rio)
library(tidyverse)
library(dplyr)
library(lavaan)
library(mgm) 
library(qgraph)
library(dplyr)
library(haven)
library(Matrix)
library(igraph)
library(NetworkComparisonTest)
library(plyr)
library(bootnet)
library(openxlsx)
library(matrixcalc)
library(IsingSampler)
library(IsingFit)
library(xtable)
library(ltm)
```

# Import MGM_G
```{r}
MGM_G <- import("../input/MGM_G.csv")
```

# Create objects
```{r}
type <- c(
  "g","g","g","g","g","g","g")

level <- c(
  1,1,1,1,1,1,1)

shortnames <- c(
  "Con",
  "LR",
  "comp_",
  "w2r_",
  "in_tr_",
  "reg_",
  "risk_")

longnames <- c(
  "Support for Conte",
  "L-R self/placement",
  "Compliance to preventive behaviors",
  "Willingness to restrict freedoms",
  "Institutional trust",
  "Support for regional system",
  "Risk perception")
```

# Fit model
```{r}
set.seed(1)
FitMGM_G <- mgm(MGM_G, type, level, k = 2, binarySign = TRUE)
```

# Preliminary graph
```{r}
#raw graph
set.seed(1)
qgraph(FitMGM_G$pairwise$wadj, 
       layout = "spring",
       theme = "colorblind",
       edge.color = FitMGM_G$pairwise$edgecolor,
       labels = shortnames, nodeNames = longnames, vsize=6.0,
       title = "Raw graph", edge.labels=FALSE, 
       legend = TRUE, legend.cex = 0.3)
```
# Community detection
```{r}
##Create function Community stability
communityStability <- function(data, type, level, iterations)
{
  
  communityMemberships <- list()
  
  for (i in 1:iterations)
  {
    fitGraph <- mgm(data, type, level, k = 2, verbatim = TRUE)
    iGraph<- graph_from_adjacency_matrix(abs
                                         (fitGraph$pairwise$wadj), "undirected", weighted =
                                           TRUE)
    communityMemberships[[i]] <- cluster_walktrap(iGraph)$membership
  }
  
  communityOverlap <- matrix(NA, length(data), length(data))
  
  for(j in 1:length(data))
  {
    
    overlapPerNode <- matrix(NA, iterations, ncol(communityOverlap))
    
    for(k in 1: iterations)
    {
      overlapPerNode[k,] <- as.numeric(communityMemberships[[k]][j] == communityMemberships[[k]])
    }
    
    communityOverlap[j,] <- apply(overlapPerNode, 2, mean)
  }
  
  diag(communityOverlap) <- 0
  
  return(list(communityMemberships = communityMemberships, communityOverlap = communityOverlap))
  
}
```

Now I apply the function. I reduce the number of iteration from 1000 to 100 
due to my limited computational power.
```{r}
#apply function
CommunityStabTotal<-communityStability(MGM_G, type, level, it=100)
```

```{r}
# Visualize community stability
qgraph(CommunityStabTotal$communityOverlap, layout = "spring", 
       theme = "colorblind", labels = shortnames,
       nodeNames = longnames,vsize=6.0,
       title = "Community Stability with indices", 
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
```

```{r}
# Vizualise detected communities
inputCommDetection_total<-CommunityStabTotal$communityOverlap
inputCommDetection_total[which(inputCommDetection_total <= .90)] <- 0

qgraph(inputCommDetection_total, layout = "spring", theme = "colorblind",
       labels = shortnames, nodeNames = longnames,vsize=6.0,
       title = "Detected communities", edge.labels=FALSE, 
       legend = TRUE, legend.cex = 0.3)
```

```{r}
# group variables based on outcome detection community stability so we can assign colors
Totalgroup_comm <- list(
 " "=c(3,4),
 " "=c(1,2,5,6,7))

# define nice colors
Totalgroup_cols <- c("#E8ED61","#8FC45A")
```

# Final Graph
```{r}
#a better graph (only communities missing)
#enables theme colorblind because we don't need to specify edge.color
inputGraphMGM_G <- FitMGM_G$pairwise$wadj
signsGraphMGM_G <- FitMGM_G$pairwise$signs
signsGraphMGM_G[which(is.na(signsGraphMGM_G))] <- 1
inputGraphMGM_G <- inputGraphMGM_G*signsGraphMGM_G

# refined, no minimum 
pdf(file = '../Output/MGM_G/MGM_G no min.pdf',paper = "USr", height = 9, width = 12)
GraphMGM_G<-qgraph(inputGraphMGM_G, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, legend = TRUE, 
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend.cex = 0.4, title = "MGM_G no min")
dev.off()
```

```{r}
# refined,  minimum = 0.5
pdf(file = '../Output/MGM_G/MGM_G min 0.05.pdf',paper = "USr", height = 9, width = 12)
GraphMGM_G<-qgraph(inputGraphMGM_G, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.05, maximum = 1, 
  details = FALSE, vsize=6.0, legend = TRUE, 
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend.cex = 0.5, title = "MGM_G min 0.05")
dev.off()
```

```{r}
# refined,  minimum = 0.10
pdf(file = '../Output/MGM_G/MGM_G min 0.10.pdf',paper = "USr", height = 9, width = 12)
GraphMGM_G<-qgraph(inputGraphMGM_G, 
  layout = "spring", theme = "colorblind", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, legend = TRUE,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend.cex = 0.5, title = "MGM_G min 0.10")
dev.off()
```

# Centrality estimates
```{r}
#graph with complete labels for centrality plot
GraphMGM_G_CENT<-qgraph(inputGraphMGM_G, 
  layout = "spring", theme = "colorblind",
  labels = longnames, minimum = 0,
  cut = 0.10, maximum = 1, details = TRUE,
  legend = FALSE, title = "Centrality table")
```
```{r}
#centrality Total
centMGM_G <- centralityTable(GraphMGM_G_CENT,standardized = FALSE)

#CentralityPlot Total
pdf('../Output/MGM_G/Centrality Table MGM_G.pdf')
centralityPlot(GraphMGM_G_CENT, include = c("Strength"),scale = "raw")
dev.off()
```

# ASPL
```{r}
#Shortest Path Lenght
SPLMGM_G <- centrality(GraphMGM_G)$ShortestPathLengths
SPLMGM_G <- SPLMGM_G[upper.tri(SPLMGM_G)]
#Average shortest path length
ASPL_MGM_G <- mean(SPLMGM_G)
```
ASPL = 8.564524

# Stability of centrality measures
Say you spot a node to be more central than other nodes. What is the stability 
of the centrality estimates? Let's assess stability of the centrality index by 
case-dropping subset bootstrap
I reduce nBoots to 100, not 1k
```{r}
set.seed(1)
MGM_G_CentStability <- bootnet(MGM_G, nBoots = 100, 
default = "mgm", type = "case",
statistics = c("Strength"), level = level, criterion="CV", binarySign=FALSE)
corStability(MGM_G_CentStability)

#plot
plot(MGM_G_CentStability, subsetRange = c(100,50), statistics = c("Strength"),
     labels = longnames)

#plot ordered
pdf('../Output/MGM_G/Centrality stability MGM_G.pdf', height = 70, width = 50)
plot(MGM_G_CentStability, "Strength", perNode = TRUE, labels = longnames,
     subsetRange = c(100,50))
dev.off()

```

# Accuracy
Say you spot a difference in edges, one thicker than the other: 
Is it meaningfully stronger? Check accuracy assess the accuracy of estimated
network connections --> Obtain confidence interval around estimated edge weight
using nonparametric bootstrapping. I reduce again the nBoots from 1k to 100

```{r}
#Edge accuracy Total
set.seed(1)
Bootnet_MGM_G<- bootnet(MGM_G, nBoots = 100, 
default = "mgm", level = level, criterion="CV", binarySign=FALSE, 
labels = longnames)

#pdf
pdf('../Output/MGM_G/Edge accuracy MGM_G.pdf', height = 50, width = 50)
plot(Bootnet_MGM_G, labels = TRUE, order = "sample", res=150)
dev.off()

```